spenv
=====

[![Build Status](https://travis-ci.org/sckott/spenv.svg)](https://travis-ci.org/sckott/spenv)

`spenv` - add environmental data to spatial data

See the [Wiki](https://github.com/sckott/spenv/wiki) for some documentation.

Package API:

* `sp_mutate` - get env data for occ data input - not ready yet
* `sp_extract_gridded` - extract env gridded data
* `sp_extract_pt` - extract env point data
* `sp_query` - query for env data - not ready yet
* `find_locs` - find locations/stations/etc. based on occ data input - internal fxn used in `sp_mutate`

## Install

```{r eval=FALSE}
devtools::install_github("ropensci/spenv")
```

```{r}
library("spenv")
```

## Example: pt env data

```{r eval=FALSE}
file <- system.file("examples", "obis_mola_mola.csv", package = "spenv")
dat <- read.csv(file)
head(dat)
```

```{r eval=FALSE}
res <- sp_extract_pt(x = dat[1:10,], radius = 100)
res[[1]]
```

## Example: gridded env data

```{r}
library("spocc")
res <- occ(query = 'Mola mola', from = 'obis', limit = 200)
res_df <- occ2df(res)
out <- sp_extract_gridded(res_df)
head(out)
```

Map it

"map"

## Contributors

* Tom Webb
* Samuel Bosch
* Scott Chamberlain

## Meta

* Please [report any issues or bugs](https://github.com/sckott/spenv/issues).
* License: MIT
